### 2016-03-17 ch03-lrm/LPMSmooth_ML_EG_JS_JL.tex
Ch03: fix some references

\researchBasedOn[This section]{Lumori2014TIM}
\TODO{figures to TikZ}
\TODO{re-introduce $F$-test truncator and box-carr averager}

@@

Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A \gls{SISO} \gls{LTI} system is considered. %, based on  \citep{Schoukens2009LPM}.
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
\begin{equation}\label{eq:lpm:TD}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer). %\JL{$G_0(q)$ represents the dynamics of the system to be estimated.}

\begin{figure}[tbh] %top bottom here
\centering
\includegraphics{\thisDir/figs/tikz0.pdf}
\caption{SISO LTI discrete-time system in an output error setup.}
\label{lpmtdrep}
\end{figure}

@@

In this section, however, a nonparametric technique is developed, %the identification problem is
formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}. The following  choices are made:

@@

\item

The work in this section is for discrete-time systems. Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.
\item

Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency.
\item

Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.

@@

The rest of the section is structured as follows. \secref{se:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
\secref{se:smoothingFRFestimate} discusses the novel smoothing method.

Ultimately, in \secref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_\text{poly}(\Omega_k)$.

@@

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{lpmleak}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}

@@

\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{eq:lpm:TD} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.

@@

The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:lpm:TD} and \eqref{lpmleak}, \emph{viz}:
\begin{equation}\label{lpm1spectra}
Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
\end{equation}
where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.

@@

Note that Assumptions \ref{ass:imprespdecay} and \ref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.

@@

According to Assumption~\ref{ass:imprespdecay}, the true impulse response tends to zero asymptotically; and by Assumption~\ref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response. The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
To this end, the following procedure is executed:

@@

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}
This is valid, as per Assumption \ref{ass:decay90perctime}.

>>>>

\researchBasedOn[This section]{Lumori2014TIM}
\TODO{figures to TikZ}
\TODO{re-introduce $F$-test truncator and box-carr averager}
\TODO{labels into standardized form}

@@

Based on \citep{Schoukens2009LPM}, the nonparametric method developed in this work is formulated in an output-error (OE) framework. A \gls{SISO} \gls{LTI} system is considered.
The input signal is a known random noise signal and the output signal is corrupted by measurement noise. This is depicted in \figref{lpmtdrep} as a linear dynamic discrete-time \gls{SISO} system, whose full mathematical model is of the form:
\begin{equation}\label{eq:nparam:trunc:LPM:TD}
y(t)=G_0(q)u_0(t)+H_0(q)e(t)=G_0(q)u_0(t)+v(t)
\end{equation}
where $G_0(q)$ represents the dynamics of the system to be estimated, $u_0(t)$ is the input signal, $v(t)= H_0(q)e(t)$ is the noise source at the output, $H_0(q)$ is the noise dynamics, $e(t)$ is white noise, and $q^{-m}$ is the backwards shift operator ($q^{-m}x(t)$ = $x(t-m)$  with $m$ a positive integer).

\begin{figure}
\centering
\includegraphics{\thisDir/figs/tikz0.pdf}
\caption{SISO LTI discrete-time system in an output error setup.}
\label{lpmtdrep}
\end{figure}

@@

In this section, however, a nonparametric technique is developed, and
formulated in the frequency domain, consistent with \citep{Pintelon2012,Mahata2006}.

The following  choices are made:

@@

\item The work in this section is for discrete-time systems. Denote the $k^{th}$ discretized frequency as $\Omega_k$ = $e^{-j2{\pi}kf_s/N}$, with $f_s$ the sample frequency and $N$ the total number of sample points.

\item  Describe the parametric plant model  $G(q,\theta)$ by the nonparametric \gls{FRF} counterpart  $G(\Omega_k)$  at the $k^{th}$ frequency.

\item Describe  the parametric noise model $H(q,\theta)$ (associated with the output noise source $v(t)$) by a nonparametric noise variance contribution $\sigma^2_v(\Omega_k)$ at the $k^{th}$ frequency.

@@

The rest of the section is structured as follows. 
\secref{se:theoryLPMandWindowing} covers the theory on the \gls{LPM} and windowing for an \gls{OE} setup.
\secref{se:smoothingFRFestimate} discusses the novel smoothing method.
Ultimately, in \secref{se:simResults}, simulation results of the following FRF estimates and their corresponding variances are compared: (i) the smooth \gls{LPM} estimate $\hat{G}_\text{sm-poly}(\Omega_k)$, (ii) the \gls{LPM} estimate $\hat{G}_\text{poly}(\Omega_k)$.

@@

Using convolution, the noiseless output signal in \figref{lpmtdrep} is $y_0(t) = g_0(t)*u_0(t)$, where the signals are sampled at $t = 0, 1, 2,...,N-1$ and the excitation signal $u_0(t)$ is random noise. As shown in \citep{Pintelon2012} and \citep{Pintelon1997} the \gls{DFT} spectra of the sampled signals at the frequency $\Omega_k$ are related as follows:
\begin{equation}\label{eq:nparam:trunc:LPM:leakage}
Y_0(k)=G_0(\Omega_k)U_0(k)+T_G(\Omega_k)
\end{equation}
where $U_0(k)$ is the \gls{DFT} spectrum of the random noise excitation,  $G_0(\Omega_k)$ is the transfer function and $T_G(\Omega_k)$ is the transients leakage term.
In this section, the \gls{DFT} of a signal $x(t)$ is defined explicitly as  \citep{Oppenheim1983}

@@

\subsubsection{The Hanning Window and the \glsentrytext{LPM}}\label{se:LPMFRFest}%\label{se:FRFhanningLPM}
\paragraph{Windowing}
The effect of windowing may be  exemplified by use of the Hanning window, which is very popular.
In a nutshell, the Hanning window is effective in reducing  the leakage errors, but  with a trade off of increased interpolation errors. %This is because the term $G_0(\Omega_k)U_0(k)$ in equation \eqref{eq:nparam:trunc:LPM:TD} is not smooth and $G_0(\Omega_k)$ varies with the frequency.
Pertinent details of the Hanning window are discussed in \citep{Schoukens2006LPM,Antoni2007FRF,Schoukens2009LPM,Wellstead1981} and \citep{Harris1978}.

@@

The \gls{DFT} spectra at the output of the \gls{SISO} system in \figref{lpmtdrep} are derived from equations \eqref{eq:nparam:trunc:LPM:TD} and \eqref{eq:nparam:trunc:LPM:leakage}, \emph{viz}:
\begin{equation}\label{lpm1spectra}
Y(k)=G_0(\Omega_k)U_0(k)+T(\Omega_k)+V_0(k)
\end{equation}
where $V_0(k) = H_0(\Omega_k)E(k)$ is a noise term, and $T(\Omega_k)$ is the leakage term. The latter is the sum of the system and the noise leakage terms, i.e. $T(\Omega_k) = T_G(\Omega_k) + T_H(\Omega_k)$.

@@

Note that \assref{ass:imprespdecay} and \assref{ass:decay90perctime} exclude the possibility of considering a system that is a pure integrator.

@@

According to \assref{ass:imprespdecay}, the true impulse response tends to zero asymptotically; and by \assref{ass:decay90perctime}, the last $10\%$ of the estimated impulse response is noise, plus a constant value due to an inaccuracy in the average value of the impulse response. The correct estimate of the mean value is obtained by shifting the whole signal such that the last $10\%$ of the impulse response is centered around 0.
To this end, the following procedure is executed:

@@

\item Obtain an estimate $\hat \sigma_\mathrm{n}$ of the standard deviation of the noise from the last 10\% of the data, \emph{viz}:
\begin{align}
\hat \sigma^2_\mathrm{n}=\frac{1}{\lceil0.1N - 1\rceil}\sum_{t=\lfloor0.9N\rfloor}^{N-1}\hat g^2(t).
\end{align}
This is valid, as per \assref{ass:decay90perctime}.

### 2016-03-17 ch03-lrm/smoothingRMSdecrease.tex
Ch03: fix some references

\begin{enumerate}
  \item The impulse response $\hat{g}_\mathrm{poly}(t)$ is split into $N_S$ segments of approximate equal lengths
$L_S = \floor{\frac{N}{N_S}}$. 
If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
  By Assumption \ref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.

@@

\end{enumerate}
%In Fig.~\ref{FRF_truncate_stat_EG}, this procedure is shown on the system depicted in \eqref{eq:systemSimulations}. 
This procedure is illustrated in Fig.~\ref{FRF_truncate_stat_EG} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)
\\
y(t) &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
% \eqref{eq:systemSimulations}. 
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $t_{\mathrm{trunc}} = 80$, beyond which all samples are set to zero, resulting in a smooth estimate.  %after which all samples are fixed to a zero value for the smoothed estimate.

\begin{figure}[tbh] %top bottom here
\centering
 \setlength\figureheight{0.6\columnwidth}
 \setlength\figurewidth{0.8\columnwidth}
  \input{truncRMS.tikz}
\caption{Schematic of statistical determination of a smooth (improved) FRF. The different segments are separated by dotted lines.}
\label{FRF_truncate_stat_EG}
\end{figure}

>>>>

\begin{enumerate}
  \item The impulse response $\hat{g}_\mathrm{poly}(t)$ is split into $N_S$ segments of approximate equal lengths
$L_S = \floor{\frac{N}{N_S}}$. 
If necessary, the length of the first segment is reduced to allow for the others to have equal lengths.
The $i^{\text{th}}$ segment is denoted $\segm{\hat{g}}{i}$, for $i \in \left\{1,\ldots,N_S\right\}$.
  By \assref{ass:decay90perctime}, the last segment, $\segm{\hat{g}}{N_S}$, is noise when $L_S \leqslant 0.1N$.

@@

\end{enumerate}
This procedure is illustrated in \figref{FRF_truncate_stat_EG} for the system described by the following simulation equations, which are relevant to the LPM outlined in Section \ref{se:LPMFRFest}:
\begin{subequations}
\label{eq:systemSimulations}
\begin{align}
y_0(t)  &= 1.5371y_0(t-1)    -0.9025y_0(t-2) + u(t)\\
y(t)       &= y_0(t) + e(t),
\end{align}
\end{subequations}
where $e(t)$ is a white noise sequence, such that the SNR of the output signal is 78.2~dB.
% \eqref{eq:systemSimulations}. 
The figure shows segments of the estimated impulse response. The last two segments are dominated by the noise, while all samples at $t<80$ have large system contributions. The algorithm outlined above selects $t_{\mathrm{trunc}} = 80$, beyond which all samples are set to zero, resulting in a smooth estimate.  %after which all samples are fixed to a zero value for the smoothed estimate.

\begin{figure}[tbh]
\centering
 \setlength\figureheight{0.6\columnwidth}
 \setlength\figurewidth{0.8\columnwidth}
  \input{truncRMS.tikz}
\caption{Schematic of statistical determination of a smooth (improved) FRF. The different segments are separated by dotted lines.}
\label{FRF_truncate_stat_EG}
\end{figure}
